Report and Figures

### 2016-11-04 figs.Rmd
checkerboard highlighted

checkerboard_illustration <- function(){
	expand.grid(x = 1:8, y = 1:8) %>%
		mutate(`(a)` = 1,
			   `(b)` = .5,
			   `(c)` = (x > 4)*1,
			   `(d)` = (x + y) %% 2) %>%
		gather(key = model, value = p, -x, -y) %>%
		ggplot(aes(x = x, y = y)) +
		ggthemes::theme_map() +
    geom_tile(aes(fill = p)) +
		scale_fill_continuous(low = 'white', high = 'black ', limits=c(0,1)) +
		facet_grid(~model, switch = 'x') +
		xlab('') +
		ylab('') +
		guides(fill=FALSE) + 
		theme(axis.ticks = element_blank(),
			  axis.text.x = element_blank(),
			  axis.text.y = element_blank(),
			  panel.margin = unit(1, "mm"),
			  panel.background = element_rect(),
			  panel.grid.major = element_line(size = 0),
			  panel.grid.minor = element_line(size = 0),
			  strip.background = element_rect(fill = "white", color = "white", size = 2),
			  plot.margin=unit(c(1,1,0,0),"mm"),
			  strip.text=element_text(vjust=-100))
}

g <- checkerboard_illustration() 
g
# g + theme(text=element_text(size=10, family="Palatino"))
ggsave('figs/checkerboard.pdf', width = 4, height = 1.3)
embed_fonts("figs/checkerboard.pdf", outfile="figs/checkerboard.pdf")
```

>>>>

overlay <- data.frame(x = 6.5, y = 4.5)

expand.grid(x = 1:8, y = 1:8) %>%
	mutate(`(a)` = 1,
		   `(b)` = .5,
		   `(c)` = (x > 4)*1,
		   `(d)` = (x + y) %% 2) %>%
	gather(key = model, value = p, -x, -y) %>%
	ggplot(aes(x = x, y = y)) +
	ggthemes::theme_map() +
  geom_tile(aes(fill = p)) +
	scale_fill_continuous(low = 'white', high = 'black ', limits=c(0,1)) +
	facet_grid(~model, switch = 'x') +
	xlab('') +
	ylab('') +
	guides(fill=FALSE) + 
	theme(axis.ticks = element_blank(),
		  axis.text.x = element_blank(),
		  axis.text.y = element_blank(),
		  panel.margin = unit(1, "mm"),
		  panel.background = element_rect(),
		  panel.grid.major = element_line(size = 0),
		  panel.grid.minor = element_line(size = 0),
		  strip.background = element_rect(fill = "white", color = "white", size = 2),
		  plot.margin=unit(c(1,1,0,0),"mm"),
		  strip.text=element_text(vjust=-100)) + 
  geom_tile(aes(x = x, y = y), color = 'red', alpha = 0, size = 0.5, data = overlay)

# g <- checkerboard_illustration() 
# g
# g + theme(text=element_text(size=10, family="Palatino"))
ggsave('figs/checkerboard.pdf', width = 4, height = 1.3)
embed_fonts("figs/checkerboard.pdf", outfile="figs/checkerboard.pdf")
```
